A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-15 MSRChallenge2016.tex
high level todos

\documentclass{sig-alternate-05-2015}
\usepackage{graphicx}
\graphicspath{ {} }

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{clegoues@cs.cmu.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software. There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an evolutionary program repair tool which applies four different kinds of possible edits to code in order to find a patch for a given bug. These changes are the following: Delete, Replace, Swap and Append.

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{color}
\usepackage{soul} 
\usepackage{booktabs}

\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}

\graphicspath{ {} }

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{clegoues@cs.cmu.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
\todo{High level todo, probably for Mau since I think it's his bibtex: please
  change the bibtex keys to take the form ``lastnameYear'', and then fix the
  citations.}
\todo{Also, please always include a non-breaking space (a tilde, look at the
  latex for an example) between a word and the cite tag, and include multiple
  references on a line in a single citation tag (again, look at the latex for an
  example; I'll do this once, but would like you to fix the rest when appropriate.}
Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically \cite{dongsun,weimer,claire,kai}, one of the
most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.
